### 2021-06-11 paper/report.tex
Finished figurenotes etc.

The reason lies in the fact that a substantial share of these tests is driven by an
elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or following
up on a positive test of a household member. The latter is essentially a form of contact
tracing, which has been shown to be very effective \citep{Contreras2021,
Kretzschmar2020}. This is also the reason for why the number of tests performed fall at
the very end of our study period. Falling infection rates mean that there are fewer
events triggering private test demand.\comment[id=HM]{Positive rates along the three
channels might be nice here, if previous comment is not a quant
story}\comment[id=K]{Working on it}\comment[id=HM]{I think there is a story in here about
risk conditional on past exposure vs. prospective risk in gatherings, but it is too late
to work through it. We might just want to calculate the
probabilities.}\comment[id=K]{Yes, we have both in the private reasons. Retrospective
after a case in the household and prospective in anticipation of participation in a
weekly meeting with friends. However, we cannot easily turn these separately on and off
at the moment as they use the same multiplier. We could, however, do this in the
future.}

@@

    \floatfoot{\noindent Note: Interventions start at Easter because there were no
        capacity constraints for rapid tests afterwards.}

@@

Figure~\ref{fig:workplace_scenarios} shows that with a large fraction of employees receiving tests, testing at the workplace has larger effects than changing requirements to work from home. Whether the share of workers working at the usual workplace is reduced or increased by ten percent hardly has an effect on infection rates. Making testing mandatory twice a week---assuming independet compliance by employers and workers or 95\% each---would have reduced infections by 13\%. Reducing rapid tests offers by employers to the level of March would have increased them by the same amount.

Despite these large effects, the results on testing likely understate the benefits.
Disadvantaged groups of the population are less likely to be reached by testing
campaigns;\comment[id=HM]{seems obvious, but I did not find anything. COSMO data? We
should get the raw data, btw.} at the same time they have a higher risk to contract
CoViD-19.\citet{RKI-Corona-Monitoring-Bundesweit}\comment[id=HM]{\url{https://www.rki.de/DE/Content/Gesundheitsmonitoring/Studien/lid/Ergebnisse.pdf}}
Mandatory tests at school and at the workplace will extend more into these groups. The
same goes for individuals who exhibit a low level of compliance with CoViD-19-related
regulations. Our analysis has shown that in the transition path to high levels of
vaccination and possibly thereafter, large-scale rapid testing can substitute for some
NPIs. This comes at a fraction of the cost. A day of the winter lockdown in Germany is
estimated to have cost 6.25~billion~Euros.\cite{Dorn2020}\comment[id=K]{This is a
prediction by the ifo Instute back from March 2020 assuming a 2 month lockdown. I did not
find anything citable that is earlier. I did find
\href{https://www.merkur.de/wirtschaft/lockdown-coronavirus-kosten-deutschland-milliarden-euro-wirtschaft-krise-zr-90231189.html}{A
quote from ifo's Timo Wollmershäuser: „Wir liegen zwischen zwei bis zweieinhalb
Milliarden Euro pro Woche“} for the winter lockdown} In early June 2021, retail prices
for self-administered rapid tests are frequently less than 1.5~Euro.\footnote{Cheapest on
\href{https://amazon.de}{Amazon} on June 11th, 2021.}

>>>>

The reason lies in the fact that a substantial share of these tests is driven by an
elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or following
up on a positive test of a household member. The latter is essentially a form of contact
tracing, which has been shown to be very effective \citep{Contreras2021,
Kretzschmar2020,FetzerGraeber2021}. This is also the reason for why the number of tests
performed fall at the very end of our study period. Falling infection rates mean that
there are fewer events triggering private test demand.\comment[id=HM]{Positive rates
along the three channels might be nice here, if previous comment is not a quant
story}\comment[id=K]{Working on it}\comment[id=HM]{I think there is a story in here
about risk conditional on past exposure vs. prospective risk in gatherings, but it is
too late to work through it. We might just want to calculate the
probabilities.}\comment[id=K]{Yes, we have both in the private reasons. Retrospective
after a case in the household and prospective in anticipation of participation in a
weekly meeting with friends. However, we cannot easily turn these separately on and off
at the moment as they use the same multiplier. We could, however, do this in the
future.}

@@

    \floatfoot{\noindent \textit{Note:} Blue lines in both figures refer to our baseline
        scenario; they are the same as in
        Figure~\ref{fig:2021_scenarios_newly_infected}. Interventions start at Easter
        because there were no capacity constraints for rapid tests afterwards.}

@@

Figure~\ref{fig:workplace_scenarios} shows that with a large fraction of employees
receiving tests, testing at the workplace has larger effects than changing requirements
to work from home. Whether the share of workers working at the usual workplace is
reduced or increased by ten percent hardly has an effect on infection rates. Making
testing mandatory twice a week---assuming independent compliance by employers and workers
or 95\% each---would have reduced infections by 13\%. Reducing rapid tests offers by
employers to the level of March would have increased them by the same amount.

Despite these large effects, the results on testing likely understate the benefits.
Disadvantaged groups of the population are less likely to be reached by testing
campaigns;\comment[id=HM]{seems obvious, but I did not find anything. COSMO data? We
should get the raw data, btw.} at the same time they have a higher risk to contract
CoViD-19.\citet{RKI-Corona-Monitoring-Bundesweit}\comment[id=HM]{\url{https://www.rki.de/DE/Content/Gesundheitsmonitoring/Studien/lid/Ergebnisse.pdf}}
Mandatory tests at school and at the workplace will extend more into these groups. The
same goes for individuals who exhibit a low level of compliance with CoViD-19-related
regulations. Our analysis has shown that in the transition path to high levels of
vaccination and possibly thereafter, large-scale rapid testing can substitute for some
NPIs. This comes at a fraction of the cost. A day of the winter lockdown in Germany is
estimated to have cost 6.25~billion~Euros.\cite{Dorn2020}\comment[id=K]{This is a
prediction by the ifo Instute back from March 2020 assuming a 2 month lockdown. I did not
find anything citable that is earlier. I did find
\href{https://www.merkur.de/wirtschaft/lockdown-coronavirus-kosten-deutschland-milliarden-euro-wirtschaft-krise-zr-90231189.html}{A
quote from ifo's Timo Wollmershäuser: „Wir liegen zwischen zwei bis zweieinhalb
Milliarden Euro pro Woche“} for the winter lockdown} In early June 2021, retail prices
for self-administered rapid tests are frequently less than 1~Euro.\comment[id=HM]{Cheapest on
\href{https://amazon.de}{Amazon} on June 11th, 2021. --- DM 95ct}
